\cvsection{Experience}

%-------------------------------------------------------------------------------
\cvsubsection{As webdeveloper}
\vspace{-3mm}

\begin{cventries}

  \cventry
    {Frontend Senior Developer}
    {Cozy Cloud}
    {Paris [FR]}
    {since jan. 2015}
    {
      \begin{cvitems}
        \item{Frontend developer in charge of rewriting main core apps (Home, Contacts, Calendar, Mail\dots) in a good quality way. Work with Backbone \textfractionsolidus Marionette, React, Vue.js, or Bacon.js. Build Ui framework foundations to improve Cozy apps development.}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Fullstack Punisher}
    {Bunkr}
    {Rouen [FR]}
    {2014}
    {
      \begin{cvitems}
        \item{Frontend developer in charge of many features in Bunkrapp, an online presentation authoring tool. Also working on API part (in Python \textfractionsolidus Flask \textfractionsolidus Celery\dots)}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Web Developer, Internal tools}
    {Clever Age}
    {Paris [FR]}
    {may 2012 - sep. 2014}
    {
      \begin{cvitems}
        \item{Frontend Developer and Backend consultant, I especially work to implement complex interfaces like "\href{http://fr.longchamp.com/pliage/personnaliser/}{Le Pliage\textsuperscript{\textregistered} Longchamp}". Work for many luxury projects with strong needs in reliability and performances. The vast majority of projects were built with a Drupal 7, or Symfony base.}
        \item{Responsible for internal tools like timesheets reporting tool, newsfeed agregator, ticketing, etc}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Freelancer}
    {MAD's Graphics - Le 11\textsuperscript{ème} Labo}
    {Paris - Rouen [FR]}
    {2008 - may 2012}
    {
      \begin{cvitems}
        \item{CEO and Lead Developer of a small Web Agency, specialized in frontend development and JS solutions.}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Web strategy}
    {Festival Automne en Normandie}
    {Rouen [FR]}
    {2007}
    {
      \begin{cvitems}
        \item{In charge of web and digital strategy.}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {IT Manager}
    {Théâtre de la Bastille}
    {Paris [FR]}
    {2005 - 2011}
    {
      \begin{cvitems}
        \item{In charge of maintenance and evolutions of equipment and solutions.}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Designer - Developer}
    {}
    {}
    {2001 - 2007}
    {
      \begin{cvitems}
        \item{Webdesign and development (frontend and backend) as non-professional.}
      \end{cvitems}
    }

\end{cventries}


%-------------------------------------------------------------------------------
\cvsubsection{As a manager - tech facilitator}
\vspace{-3mm}

\begin{cventries}

  \cventry
    {Mentor and tech support}
    {Cozy Cloud}
    {Paris [FR]}
    {since jan. 2015}
    {
      \begin{cvitems}
        \item{In charge of technical support and mentorship program for teammates and community fellows for front-end contributions. Organize hiring processes and interviews. Help day-to-day relations in a remote-full context.}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Tech evangelist}
    {Conferences}
    {France}
    {since 2012}
    {
      \begin{cvitems}
        \item{Technical speaker in many conferences, about frontend development, code quality, and team processes.}
      \end{cvitems}
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Teacher}
    {CESI}
    {Paris [FR]}
    {2009 - 2012}
    {
      \begin{cvitems}
        \item{Teacher in CESI, IT high school. Teacher for Web technologies, networks in software and Unix/Linux plateforms.}
      \end{cvitems}
    }

\end{cventries}
