\cvsection{Skills}

\begin{cventries}

  \cventry
    {Frontend Senior Developer}
    {Development}
    {}
    {}
    {
      Deep knowledge of \textbf{ES5} / \textbf{ES6}, \textbf{HTML}, \textbf{CSS} (and pre/post-processors); with a strong use of \textbf{ARIA} to build huge, performant and reactive interfaces. Experienced with \textbf{Node.js} and \textbf{PHP}; comfortable with \textbf{Ruby}, \textbf{Python}. Used to many frameworks, like \textit{React}, \textit{Vue.js}, \textit{Drupal}, \textit{Symfony} and \textit{Silex}, \textit{RoR}, \textit{Flask}…
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Mentor \& Tech Evangelist}
    {Management and evangelism}
    {}
    {}
    {
      Daily facilitator for his fellows, helping by providing support to the rest of the community and his teammates. Mentor and referent in mentorship progam, I also manage and supervise hiring processes and interviews. I deliver my knowledge in many conferences as an experienced speaker.
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Ui integrator}
    {UX \cdotp Design}
    {}
    {}
    {
      Really attached to beautiful and smart interfaces. I'm comfortable with typography, design softwares (bitmaps and vectors editors), and prototyping. Love working on interfaces designs, with accesibility in mind.
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Devops and system administration}
    {Systems}
    {}
    {}
    {
      High knowledge of Unix systems, and comfortable with OS X, Linux, BSD\dots Really interested in processes and quality. Also comfortable with toolchain solutions, from frontend needs to backend integrations.
    }
  \vspace{\msetCventryBottomSkip}

  \cventry
    {Day-to-day projects}
    {Environment}
    {}
    {}
    {
      Daily use of Git and CI environment (Travis, Jenkins\dots) Working with \textit{Scrum} agility principles in mind.
    }

\end{cventries}
